Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
first cut at the conclusion; very draft

\section{Conclusions and Future Work}\label{sec:conc}

%\section*{Acknowledgments}
%include only after review.

@@

% \begin{appendices}
% 	\section{Other data that might be interesting to report}
% 	This section has the only purpose of presenting and discussing other data that
% 	are not intended yet to be used in the paper. If you find something interesting
% 	in this block of information, please report.
%
% 	\begin{table}[h]
% 		\centering
% 		\setlength{\tabcolsep}{4pt}
% 		\begin{tabular}{ccc}
% 			\toprule
% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
% 			\midrule
% 			$<0$  & 19.2\% & 15.4\% \\
% 			$=0$  & 23.1\% & 26.9\% \\
% 			$>0$  & 57.7\% & 57.7\% \\
%
% 			\bottomrule
% 		\end{tabular}
% 		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
% 		\label{tab:diagchart}
% 	\end{table}
% 	\normalsize
%
% 	\begin{table}[h]
% 		\centering
% 		\setlength{\tabcolsep}{4pt}
% 		\begin{tabular}{ccc}
% 			\toprule
% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
% 			\midrule
% 			$<0$  & 40.7\% & 33.3\% \\
% 			$=0$  & 25.9\% & 18.5\% \\
% 			$>0$  & 33.3\% & 48.1\% \\
%
% 			\bottomrule
% 		\end{tabular}
% 		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
% 		\label{tab:diagtime}
% 	\end{table}
% 	\normalsize
%
%
% 	\begin{table}[h]
% 		\centering
% 		\setlength{\tabcolsep}{4pt}
% 		\begin{tabular}{ccc}
% 			\toprule
% 			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
% 			\midrule
% 			$<0$  & 36.8\% & 28.9\% \\
% 			$=0$  & 26.3\% & 28.6\% \\
% 			$>0$  & 36.8\% & 50.0\% \\
%
% 			\bottomrule
% 		\end{tabular}
% 		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
% 		\label{tab:diagmockito}
% 	\end{table}
% 	\normalsize
%
% 	\begin{table*}[h]
% 		\setlength{\tabcolsep}{3pt}
% 		\begin{tabular}{llllllllllllll}
% 			\toprule
% 			   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
% 		top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
% 		top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
% 			   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
% 		top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
% 		top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
% 			\bottomrule
% 		\end{tabular}
% 		\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
% 		\label{table:reduction}
% 	\end{table*}
%
% 	\begin{table*}[h]
% 		\small
% 		\setlength{\tabcolsep}{3pt}
% 		\begin{tabular}{@{}p{1.6cm}p{1cm}p{1.3cm}p{1cm}p{1cm}p{0.8cm}p{1cm}p{1cm}p{1cm}p{1.1cm}p{1cm}p{1cm}p{1.6cm}p{1.3cm}@{}}
% 		\toprule
% 			   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
% 		SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
% 		\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
% 		$\Delta-5$  & 56.94\% & -169.80\%   & 23.08\%     & 38.15\% & 6.67\%      & 73.68\% & 38.89\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12258.97\% & 20.22\%   \\
% 		\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
% 		$\Delta-10$ & 1.39\%  & -53.02\%    & 23.08\%     & 34.10\% & 6.67\%      & 73.68\% & 36.11\% & 15.79\% & 0.00\%      & 20.00\% & 40.00\% & -12453.85\% & 20.22\%   \\\midrule
% 		& 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
% 		SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
% 		\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
% 		$\Delta-5$  & 0.00\%  & 8.78\%      & 32.10\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 46.15\% & -84.27\%    & 0.00\%  & 0.00\%  & -71.97\%    & -412.14\% \\
% 		\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
% 		$\Delta-10$ & 0.00\%  & 8.35\%      & 19.75\%     & 0.00\%  & 19.30\%     & 28.57\% & 0.00\%  & 24.36\% & -84.27\%    & 0.00\%  & 0.00\%  & -72.45\%    & 0.00\% \\
% 		\bottomrule
% 		\end{tabular}
% 		\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 ($\Delta-5$) and top-10 ($\Delta-10$) of the faulty classes}
% 		\label{table:performance}
% 	\end{table*}
% 	\normalsize

% \end{appendices}

>>>>

\section{Conclusions and Future Work}
\label{sec:conc}
%
Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (DS)
and Spectrum-based Fault Localization (SFL) are very popular fault diagnosis t
echniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining DS with SFL. The results of our empirical study show that, in
practice, DS rarely misses faulty statements (23 misses in 260 cases) and that
the DS-SFL combination improves the diagnostic accuracy in 51\% of the faults.
Hence, we found that, despite tacit opinions of the research community about
the usefulness of DS in automated debugging, we found the combination practical
and effective, and encourage new SFL techniques to be evaluated against that
optimization.

Future work is as follows: bla bla.

%
%\section*{Acknowledgments}
%include only after review.

@@
